### 2024-03-26 appendix_exp6.Rmd
major changes before adding analytical part

We manipulated convergence within participants in the same way we did in experiment 4. In addition, between participants, we manipulated the number of choice options. Participants were randomly assigned to either to see stimuli with '3' options, or with '10' options. Participants assigned to the '10' options condition, participants were assigned to one of two distinct sub-conditions: one in which the range of the answers corresponds to the range of the '3' options condition, and another with increased range (see Appendix XX). We added the increased range condition because we anticipated the possibility that participants might not consider all options as relevant when they only see scenarios in which all answers cluster. We found no differences between the two sub-conditions and collapsed them into a single '10' options condition.

```{r stimuli-options, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(
  imgage_a = c("![](stimuli/Experiment_6/stimuli_Exp6/consensus_3_a.png){ width=60% }"),
  imgage_b = c("![](stimuli/Experiment_6/stimuli_Exp6/consensus_10_a.png){ width=60% }")
  )

@@

```{r stimuli-10, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(
  condition = c("opposing majority (0)", "dissensus (1)", "majority (2)", "consensus (10)"),
  imgage_a = c(
    "![](Experiment_6/figures/stimuli/minority_10_a.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/divergence_10_a.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/majority_10_a.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/consensus_10_a.png){ width=60% }"
  ),
  imgage_b = c(
    "![](Experiment_6/figures/stimuli/minority_10_b.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/divergence_10_b.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/majority_10_b.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/consensus_10_b.png){ width=60% }"
  )
)

# Use kable() to create the table and print it as Markdown
kableExtra::kable(image_paths, format = "markdown",
                  col.names = c("Level", "Version a)", "Version b)"), 
                  align = "c",
                  caption = "Stimuli for 10 options condition by levels of convergence")

@@

```{r stimuli-10-alt, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(
  condition = c("opposing majority (0)", "dissensus (1)", "majority (2)", "consensus (10)"),
  imgage_a = c(
    "![](Experiment_6/figures/stimuli/minority_10_a_alt.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/divergence_10_a_alt.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/majority_10_a_alt.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/consensus_10_a_alt.png){ width=60% }"
  ),
  imgage_b = c(
    "![](Experiment_6/figures/stimuli/minority_10_b_alt.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/divergence_10_b_alt.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/majority_10_b_alt.png){ width=60% }",
    "![](Experiment_6/figures/stimuli/consensus_10_b_alt.png){ width=60% }"
  )
)

@@

>>>>

The main focus of experiment 6 was on comparing 3-options conditions to 10-options conditions (see Table \@ref(tab:stimuli-options)). Additionally, we varied between two versions of the 10-options conditions: one in which the range of the answers corresponded to the range of the three options condition (see Table \@ref(tab:stimuli-10)), and another with increased range (see Table \@ref(tab:stimuli-10-alt)).

```{r stimuli-options, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(
  imgage_a = c("![](stimuli/Experiment_6/stimuli_Exp6/consensus_3_a.png){ width=40% }"),
  imgage_b = c("![](stimuli/Experiment_6/stimuli_Exp6/consensus_10_a.png){ width=40% }")
  )

@@

```{r stimuli-10, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(
  condition = c("opposing majority (0)", "dissensus (1)", "majority (2)", "consensus (10)"),
  imgage_a = c(
    "![](Experiment_6/figures/stimuli/minority_10_a.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_a.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_a.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_a.png){ width=40% }"
  ),
  imgage_b = c(
    "![](Experiment_6/figures/stimuli/minority_10_b.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_b.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_b.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_b.png){ width=40% }"
  )
)

# Use kable() to create the table and print it as Markdown
kableExtra::kable(image_paths, format = "markdown",
                  col.names = c("Level", "Version a)", "Version b)"), 
                  align = "c",
                  caption = "Stimuli for 10 options condition by levels of convergence", 
                  full_width = T) %>%
  column_spec(1, width = "2em") %>%
  column_spec(2, width = "20em") %>%
  column_spec(3, width = "20em") %>%
  # make smaller to fit
  kable_styling(latex_options = "scale_down")

@@

```{r stimuli-10-alt, echo=FALSE}
# Create a matrix of image file paths as Markdown-formatted strings
image_paths <- data.frame(
  condition = c("opposing majority (0)", "dissensus (1)", "majority (2)", "consensus (10)"),
  imgage_a = c(
    "![](Experiment_6/figures/stimuli/minority_10_a_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_a_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_a_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_a_alt.png){ width=40% }"
  ),
  imgage_b = c(
    "![](Experiment_6/figures/stimuli/minority_10_b_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/divergence_10_b_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/majority_10_b_alt.png){ width=40% }",
    "![](Experiment_6/figures/stimuli/consensus_10_b_alt.png){ width=40% }"
  )
)

@@

## Comparison with simulation

```{r}
# read simulated data from .csv files
data_3_options <- read_csv("Experiment_4/data/sim_vary_options_3_sample.csv")
```

Since we didn't find a difference between three and ten choice option scenarios in the participant data, we wanted to have a normative point of reference of what should have been the expected difference, given our model. We therefor compared participant ratings to observed values from simulated data. The data was generated using the model described in the main paper, and assuming a uniform competence distribution. Compared to this data generating model, participants considerably underestimated how the number of choice options alters the effect of convergence for both accuracy and competence. Table \@ref(tab:model-vs-participant-table) compares the results of regressions on participant data and regressions on simulated data. Fig. \@ref(fig:exp6-model) visualizes the results.

```{r}
# possible analysis for varying choice options (3 vs. 10)
regression_data <- data_3_options %>%
  filter(options %in% c(3, 10)) %>%
  # group_by(iteration, constellation, options) %>%
  # summarise(across(c(average_accuracy, average_relative_competence), mean)) %>%
  mutate(
    convergence = case_when(
      constellation == "minority(ies)" ~ 0,
      constellation == "dissensus" ~ 1,
      constellation == "majority" ~ 2,
      constellation == "consensus" ~ 3),
    # make a categorical version
    convergence_categorical = recode_factor(convergence, 
                                            `0` = "minority", 
                                            `1` = "divergence", 
                                            `2` = "majority", 
                                            `3` = "consensus",
                                            .default = NA_character_),
    # make a version of number for plot
    number_options = ifelse(options == 3, "three", "ten"),
    # we'll use an effect coded version for the analysis
    number_options_effect_code = ifelse(options == 3, -0.5, 0.5),
    # scale accuracy to reach from 0 to 100 (instead from 0 to 1)
    average_accuracy = average_accuracy*100,
    # scale competence to reach from 1 to 7 (instead of 0 to 1)
    average_relative_competence = 6*average_relative_competence + 1
  )

accuracy <- lm(average_accuracy ~ convergence + number_options_effect_code + convergence*number_options_effect_code,
               data = regression_data)
competence <- lm(average_relative_competence ~ convergence + number_options_effect_code + convergence*number_options_effect_code, 
                 data = regression_data)
```

```{r}
# read data
exp6 <- read_csv("Experiment_6/data/cleaned.csv") %>% 
  # import experimental variable as factor and set levels
  mutate(
    # set levels for `convergence`
    convergence_categorical = recode_factor(convergence, 
                                            `0` = "minority", 
                                            `1` = "divergence", 
                                            `2` = "majority", 
                                            `3` = "consensus",
                                            .default = NA_character_))  %>% 
  # For this model, we effect code `number_options`, so that we get a coefficient 
  # for the main effect of convergence as well as for the interaction
  mutate(number_options_effect_code = recode(number_options, "three" = -0.5, "ten" = +0.5))

# run mixed model (random slope and intercept) with participants as random factor
exp6_model_accuracy = lmer(accuracy ~ convergence + number_options_effect_code + 
                            number_options_effect_code*convergence + (1 + convergence | id), 
                       data = exp6)
exp6_model_competence = lmer(competence ~ convergence + number_options_effect_code + 
                            number_options_effect_code*convergence + (1 + convergence | id), 
                       data = exp6)
```

```{r}
modelsummary::modelsummary(list("Accuracy" = exp6_model_accuracy, 
                                "Competence" = exp6_model_competence,
                                "Accuracy" = accuracy, 
                                "Competence" = competence
                                ),
                           title = 'Participants vs. Model (Exp. 6)', 
                           stars = TRUE) %>%
  kableExtra::add_header_above(c(" " = 1, "Participants" = 2, "Model" = 2))
```

(ref:exp6-model) Comparison of accuracy (top) and competence (bottom) ratings in participant data (left) to observations in simulated data (right), by level of convergence.

```{r exp6-model, fig.cap="(ref:exp6-model)"}
# colors were identified with the wesanderson package (library(wesanderson)) as:
# wes_palette("Zissou1", 100, type = "continuous")[A number]

# plot for accuracy
plot_accuracy_participants <- ggplot(exp6,
       aes(x = convergence_categorical, y = accuracy, fill = number_options)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .4,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 2, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy", fill = NULL, title = "Participants") +
  scale_fill_manual(values = c("#EE3800", "#3D9BB2"), 
                    name = "Number of choice options: ") +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

plot_accuracy_model <- ggplot(regression_data,
       aes(x = convergence_categorical, y = average_accuracy, fill = number_options)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .4,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 2, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy", fill = NULL, title = "Model") +
  scale_fill_manual(values = c("#EE3800", "#3D9BB2"), 
                    name = "Number of choice options: ") +
  guides(fill = "none") +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

# plot for competence
plot_competence_participants <- ggplot(exp6,
       aes(x = convergence_categorical, y = competence, fill = number_options)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .4,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 2, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Competence", fill = NULL) +
  scale_fill_manual(values = c("#EE3800", "#3D9BB2")) +
  guides(fill = "none") +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

plot_competence_model <- ggplot(regression_data,
       aes(x = convergence_categorical, y = average_competence, fill = number_options)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .4,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 2, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Competence", fill = NULL) +
  scale_fill_manual(values = c("#EE3800", "#3D9BB2")) +
  guides(fill = "none") +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

participants <- ggpubr::ggarrange(plot_accuracy_participants,plot_accuracy_model, common.legend = TRUE) 
model <- ggpubr::ggarrange(plot_competence_participants, plot_competence_model)

participants / model + plot_layout(guides = "collect")
```

### 2024-03-26 appendix_simulations.Rmd
major changes before adding analytical part

# Simulations {simulations}

@@

We suppose that individual competence levels are drawn from a competence distribution, which can be expressed by a beta distribution. This competence distribution can take vary different shapes, depending on the alpha and beta parameters that describe the distribution (see fig. \@ref(fig:competence-distributions)).

We draw an estimate for each individual based on their respective competence distribution. For each individual, we then measure accuracy as the (squared) distance between their estimate and the true answer. Having a competence and an accuracy value for each individual, we randomly assign individuals to groups of three. For each group, we calculate the average of the three individuals' competence and accuracy. We measure the convergence of a group by calculating the standard deviation of the estimates. We run this simulation on a sample size of roughly 100000 (varying slightly as a function of sample size). We repeat this simulation process for various sample sizes and competence distributions. The results are displayed in Fig. \@ref(fig:simulation-accuracy-numeric-1) to \@ref(fig:simulation-accuracy-numeric-6), for accuracy, and Fig. \@ref(fig:simulation-competence-numeric-1) to \@ref(fig:simulation-competence-numeric-6), for competence. Across all underlying competence distributions, we find a positive correlation between convergence and accuracy, which tends towards 1 as sample size increases (see Fig. \@ref(fig:simulation-numeric-correlations)). As for accuracy, we find a positive correlation between convergence and competence across all underlying competence distributions. However, this correlations are weaker than for accuracy, and do not increase with sample size (see Fig. \@ref(fig:simulation-numeric-correlations)).

@@

@@

As for the numeric scenario, we ran simulations to provide a normative answer as to whether it is justified to infer accuracy and competence from greater convergence. We, again, suppose that an individual's answer is drawn from an internal distribution - in this case, a multinomial distribution, that describes how likely the individual is to choose each available option. If there are m choice options, an individual has the probability p of picking the right one, and the probability of (1-p)/(m-1) to pick any other option. Each individual has their own multinomial distribution. We define competence as the probability of making the correct choice. The higher the competence, the greater the probability that an individual will choose the correct option. Competence values range from being at chance for selecting the correct option (p = 1/m) to certainly selecting the correct option (p = 1). As before in the numeric case, suppose that individual competence levels are drawn from a competence distribution, which can be expressed by a beta distribution (see fig. \@ref(fig:competence-distributions)). Based on their competence level, we draw an estimate for each individual. We measure an individual's accuracy as a binary outcome, namely whether they picked the correct option, or not. We then randomly assign individuals to groups of informants (we vary the sample size from one simulation to another). Within these groups, we calculate the share of individuals voting for an answer option. For example, in a scenario in which three individuals pick among three options (A, B and C), two individuals might vote C and one B. In this case we obtain an average accuracy and an average competence value for a share of 2/3 (option C) and for a share of 1/3 (option B). We simulate this on a population of 999000 individuals. We repeat this procedure varying the underlying population competence distributions, and additionally varying either (a) the sample size of informants, or (b) the number of choice options. If we vary the sample size, we hold the number of choice options constant at n = 3, and vice versa when varying the number of choice options. Fig. \@ref(fig:simulation-accuracy-sample-categorical) shows the average accuracy, and Fig. \@ref(fig:simulation-competence-sample-categorical) the average competence value for each share of votes, for different competence levels and varying the sample size. Fig. \@ref(fig:simulation-accuracy-options-categorical) and Fig. \@ref(fig:simulation-competence-options-categorical) display the same relationship, but varying the number of choice options instead. The figures dispaly that, across all sample sizes and competence levels, the larger the share of votes for an option, the more accurate the option is on average. That relationship appears to follow some sigmoid curve which switches from an average accuracy of 0 to an average accuracy of 1 before a share of 0.5 is attained, and which is steeper for larger sample sizes. For competence, we observe a similar sigmoid-like relationship, but of lesser amplitude and varying considerably as a function of the underlying population competence distributions.

@@

```{r simulation-accuracy-numeric-1, fig.cap="(ref:simulation-accuracy-numeric)", out.width="75%"}
# plot_list <- plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")
# ggarrange(plotlist = plot_list, common.legend = TRUE, ncol = 1)

plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[1]]
```

```{r simulation-accuracy-numeric-2, fig.cap="(ref:simulation-accuracy-numeric)", out.width="75%"}
plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[2]]
```

```{r simulation-accuracy-numeric-3, fig.cap="(ref:simulation-accuracy-numeric)", out.width="75%"}
plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[3]]
```

```{r simulation-accuracy-numeric-4, fig.cap="(ref:simulation-accuracy-numeric)", out.width="75%"}
plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[4]]
```

```{r simulation-accuracy-numeric-5, fig.cap="(ref:simulation-accuracy-numeric)", out.width="75%"}
plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[5]]
```

```{r simulation-accuracy-numeric-6, fig.cap="(ref:simulation-accuracy-numeric)", out.width="75%"}
plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[6]]
```

@@

```{r simulation-competence-numeric-1, fig.cap="(ref:simulation-competence-numeric)", out.width="75%"}
# plot_list <- plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")
# ggarrange(plotlist = plot_list, common.legend = TRUE, ncol = 1)
plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[1]]
```

```{r simulation-competence-numeric-2, fig.cap="(ref:simulation-competence-numeric)", out.width="75%"}
plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[2]]
```

```{r simulation-competence-numeric-3, fig.cap="(ref:simulation-competence-numeric)", out.width="75%"}
plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[3]]
```

```{r simulation-competence-numeric-4, fig.cap="(ref:simulation-competence-numeric)", out.width="75%"}
plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[4]]
```

```{r simulation-competence-numeric-5, fig.cap="(ref:simulation-competence-numeric)", out.width="75%"}
plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[5]]
```

```{r simulation-competence-numeric-6, fig.cap="(ref:simulation-competence-numeric)", out.width="75%"}
plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[6]]
```

>>>>

# Simulations {#simulations}

@@

We suppose that individual competence levels are drawn from a competence distribution, which can be expressed by a beta distribution. This competence distribution can take vary different shapes, depending on the alpha and beta parameters that describe the distribution (see Fig. \@ref(fig:simulations)).

We draw an estimate for each individual based on their respective competence distribution. For each individual, we then measure accuracy as the (squared) distance between their estimate and the true answer. Having a competence and an accuracy value for each individual, we randomly assign individuals to groups of three. For each group, we calculate the average of the three individuals' competence and accuracy. We measure the convergence of a group by calculating the standard deviation of the estimates. We run this simulation on a sample size of roughly 99900 (varying slightly as a function of sample size). We repeat this simulation process for various sample sizes and competence distributions. The results are displayed in Fig. \@ref(fig:simulation-accuracy-numeric) for accuracy, and Fig. \@ref(fig:simulation-competence-numeric) for competence. Across all underlying competence distributions, we find a positive correlation between convergence and accuracy, which tends towards 1 as sample size increases (see Fig. \@ref(fig:simulation-numeric-correlations)). As for competence, we find a positive correlation between convergence and competence across all underlying competence distributions. However, these correlations are weaker than for accuracy, and do not increase with sample size (see Fig. \@ref(fig:simulation-numeric-correlations)).

(ref:simulation-numeric-correlations) Correlation between the convergence of the answers of a group of agents and (left) the average accuracy of their answers; (right) the average competence of the agents, as a function of how many agents are in the group, and of the competence distribution of the agents (see Fig. \@ref(fig:simulations)).

```{r simulation-numeric-correlations, fig.cap="(ref:simulation-numeric-correlations)", out.width="75%"}
# calculate correlations
simulation_numeric <- simulation_numeric %>% 
  group_by(competence, sample) %>% 
  mutate(correlation_accuracy = cor(accuracy_mean, convergence), 
         correlation_competence = cor(competence_mean, convergence)) %>% 
  ungroup()

# accuracy plot
accuracy_plot <- ggplot(simulation_numeric, aes(x = sample, y = correlation_accuracy, color = competence)) +
  geom_point() + 
  geom_line(alpha = 0.5) + 
  labs(y = "Correlation \nAccuracy/Convergence", 
       x = "Group size", 
       color = "Competence distribution") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_color_brewer(palette = "Set1") +
  plot_theme + 
  theme(
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8)) +
  rremove("xlab")

# competence plot
competence_plot <- ggplot(simulation_numeric, aes(x = sample, y = correlation_competence, color = competence)) +
  geom_point() + 
  geom_line(alpha = 0.5) + 
  labs(y = "Correlation \nCompetence/Convergence", 
       x = "Group size", 
       color = "Competence distribution") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_color_brewer(palette = "Set1") +
  plot_theme + 
  theme(
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8)) +
  rremove("xlab")

ggarrange(accuracy_plot, competence_plot, common.legend = TRUE) %>% 
    annotate_figure(bottom = textGrob("Group size", gp = gpar(cex = 1, fontface = "bold")))
```

@@

(ref:simulation-accuracy-sample-categorical) Accuracy as a function of convergence, for different population competence distributions and sample sizes. The number of choice options is three.

```{r simulation-accuracy-sample-categorical, fig.cap="(ref:simulation-accuracy-sample-categorical)", out.width="100%"}
plot_competence_vary_relative_majority_categorical(simulation_sample_categorical,
                                       outcome = "Accuracy", variable = sample) 
```

(ref:simulation-competence-sample-categorical) Competence as a function of convergence (i.e. vote share for an option), for different population competence distributions and sample sizes. The number of choice options is three.

```{r simulation-competence-sample-categorical, fig.cap="(ref:simulation-competence-sample-categorical)", out.width="100%"}
plot_competence_vary_relative_majority_categorical(simulation_sample_categorical,
                                       outcome = "Competence", variable = sample)
```

@@

As for the numeric scenario, we ran simulations to provide a normative answer as to whether it is justified to infer accuracy and competence from greater convergence. We, again, suppose that an individual's answer is drawn from an internal distribution - in this case, a multinomial distribution, that describes how likely the individual is to choose each available option. If there are m choice options, an individual has the probability p of picking the right one, and the probability of (1-p)/(m-1) to pick any other option. Each individual has their own multinomial distribution. We define competence as the probability of making the correct choice. The higher the competence, the greater the probability that an individual will choose the correct option. Competence values range from being at chance for selecting the correct option (p = 1/m) to certainly selecting the correct option (p = 1). As before in the numeric case, suppose that individual competence levels are drawn from a competence distribution, which can be expressed by a beta distribution (see Fig. \@ref(fig:simulations)). Based on their competence level, we draw an estimate for each individual. We measure an individual's accuracy as a binary outcome, namely whether they picked the correct option, or not. We then randomly assign individuals to groups of informants (we vary the sample size from one simulation to another). Within these groups, we calculate the share of individuals voting for an answer option. For example, in a scenario in which three individuals pick among three options (A, B and C), two individuals might vote C and one B. In this case we obtain an average accuracy and an average competence value for a share of 2/3 (option C) and for a share of 1/3 (option B). We simulate this on a population of 99900 individuals. We repeat this procedure varying the underlying population competence distributions, and additionally varying either (a) the sample size of informants, or (b) the number of choice options. If we vary the sample size, we hold the number of choice options constant at n = 3, and vice versa when varying the number of choice options. Fig. \@ref(fig:simulation-accuracy-sample-categorical) shows the average accuracy, and Fig. \@ref(fig:simulation-competence-sample-categorical) the average competence value for each share of votes, for different competence levels and varying the sample size. Fig. \@ref(fig:simulation-accuracy-options-categorical) and Fig. \@ref(fig:simulation-competence-options-categorical) display the same relationship, but varying the number of choice options instead. The figures display that, across all sample sizes and competence levels, the larger the share of votes for an option, the more accurate the option is on average. That relationship appears to follow some sigmoid curve which switches from an average accuracy of 0 to an average accuracy of 1 before a share of 0.5 is attained, and which is steeper for larger sample sizes. For competence, we observe a similar sigmoid-like relationship, but of lesser amplitude and varying considerably as a function of the underlying population competence distributions.

@@

```{r, simulation-accuracy-numeric, fig.cap="(ref:simulation-accuracy-numeric)", fig.height= 10, fig.width=10}
plot_continuous_combined(data = simulation_numeric, outcome = "accuracy")
```

@@

```{r, simulation-competence-numeric, fig.cap="(ref:simulation-competence-numeric)", fig.height= 10, fig.width=10}
plot_continuous_combined(data = simulation_numeric, outcome = "competence")
```

```{r simulation-accuracy-single, fig.cap="(ref:simulation-accuracy-single)", out.width="75%"}
# plot_list <- plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")
# ggarrange(plotlist = plot_list, common.legend = TRUE, ncol = 1)

# Display single plots
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[1]]
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[2]]
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[3]]
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[4]]
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[5]]
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "accuracy")[[6]]
```

```{r simulation-competence-single, fig.cap="(ref:simulation-competence-single)", out.width="75%"}
# plot_list <- plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")
# ggarrange(plotlist = plot_list, common.legend = TRUE, ncol = 1)

# Display single plots
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[1]]
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[2]]
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[3]]
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[4]]
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[5]]
# plot_competence_vary_numeric(data = simulation_numeric, outcome = "competence")[[6]]
```
